Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-04-06 journal-draft/bare_jrnl_comsoc.tex
Erwin looked briefly into the first proof and started to correct the second proof.

After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$. %, which is smaller than all the possible individual connectivity degrees in the CR network.
Then $i$ broadcasts its new individual connectivity degree to all its neighbors. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
We manipulate the individual connectivity degree of the CR nodes which are included in certain clusters. Hence, nodes located outside of the a formed cluster can possibly become cluster heads or can also be included into other clusters.
When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to $M$.
%Then every CR node becomes either cluster head or one member of at least one cluster.
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
%Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, that secondary user will eventually be integrated into a certain cluster, or it eventually becomes a cluster head.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, every secondary user is included into at least one cluster within $N$ steps.
\end{theorem}
Here, \textit{Step} means one secondary user conducts Algorithm~\ref{clustering:theorem} once.
The Proof is in Appendix~\ref{proof_clustering:theorem}.
According to Theorem~\ref{clustering:theorem}, we can assign reasonable amount of time for phase I to complete.

%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
Node $B$ and $H$ have the same individual connectivity degree, $d_B=d_H$, but as $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C_H$ is $\{H, B, A, G\}$.

@@

\section*{Proof of Theorem~\ref{clustering:theorem}}
\label{proof_clustering:theorem}
\begin{proof}
%Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
We consider a CRN which can be represented as a connected graph.
To simplify the discussion, we assume the secondary users have unique individual connectivity degrees, and they have identical ID and social connectivity degrees.
This assumption is fair as the social connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics.

%we assume every node has at least one neighbour.
Assuming there exist some secondary users which are not included into any cluster, and node $\alpha$ is of this kind.
As node $\alpha$ is not contained in any cluster, there must be at least one node $\beta\in \text{Nb}_\alpha$, with $d_{\alpha} > d_{\beta}$.
Otherwise, node $\alpha$ is eligible to form a cluster.
If node $\beta$ becomes cluster head, node $\alpha$ is included.
If node node $\beta$ is not cluster head, i.e., $\beta$ is not in any cluster, we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
When no cluster head appears, this series of nodes with monotonically decreasing $d_i$ might continue to grow, but finally ceases when either the individual connectivity degree is zero, or every secondary node has already been in the series of nodes.
An example of the formed node series is shown as Figure~\ref{lemma1}.

@@

Now we find the node $\omega$ is in the end of this series.
As $\omega$ is the end node and does not have neighbouring nodes with lower individual connectivity degree $D$, $\omega$ becomes cluster head and incorporate all its one-hop neighbours, including the node before it in the series (here we assume that every new formed cluster has common channels).
After that, the node recruited into cluster will set its connection degree $D$ to $M$, which enables the node further down in the list to become a cluster head.
In this way, all the nodes in the series are in at least one cluster in the inverse sequence.
This result contradicts the initial assumption and proves the claim stated above.
Meanwhile, through this proof, we know that within at most $N$ steps, all the nodes belong to certain clusters.
\end{proof}

@@

Given a set $\mathcal{G}$ which contains finite number of positive integers, and a collection of set $\mathcal{Q}=\{s_1,s_2,\cdots,s_m\}$, where for each element $s_r, 1\leq r \leq m$, there is $s_r\subseteq \mathcal{G}$, $ 1\leq|s_r| \leq k$, and $s_r$ has an associated weight which is positive real number.
The question is whether exists a collection $\mathcal{S}\subseteq \mathcal{Q}$, where $\mathcal{S}$ contains only disjoint sets and the total weight of sets in $\mathcal{S}$ is greater than $\lambda$.
Weighted k-set packing is NP-hard when $k\geqslant 3$.~\cite{Computers_a_Intractability}
\end{mydef}

To prove the centralized clustering problem is of NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is as hard as the later.
%, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
To complete the reduction, we need to conduct following two steps:
\begin{itemize}
\item step 1: Show there exists a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
\item step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
\end{itemize}

We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
Let set $\mathcal{G}$ contain $N$ natural numbers which are from 1 to $N$.
$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$.
Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$.
%As the number of common channel of clusters is always integer
%give new weight to them in following way

>>>>

After receiving the notification from a cluster head, a CR node $i$ is aware that it becomes a member of a cluster. Consequently, $i$ sets its individual connectivity degree to a positive number $M > |\mathcal{K}| \cdot N$. %, which is smaller than all the possible individual connectivity degrees in the CR network.
Then $i$ broadcasts its new individual connectivity degree to all its neighbors. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
We manipulate the individual connectivity degree of the CR nodes which are included in certain clusters. Hence, nodes located outside of the a formed cluster can possibly become cluster heads or can also be included into other clusters.
When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to $M$.
%Then every CR node becomes either cluster head or one member of at least one cluster.
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
%Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
We have the following theorem to show that as long as a secondary user's individual connectivity degree is greater than zero, that secondary user will eventually be integrated into a certain cluster, or it eventually becomes a cluster head.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, every secondary user is included into at least one cluster within $N$ steps. (COMMENT: $N$ has to be defined within the theorem!!)
\end{theorem}
Here, by \textit{step} we mean one application of Algorithm~\ref{clustering:theorem} by a secondary user.
The Proof is in Appendix~\ref{proof_clustering:theorem}.
According to Theorem~\ref{clustering:theorem}, Phase I completes within a reasonable amount of time.

%This judgement is conducted periodically, and phase I ends after every node ascertains it is cluster head or not.
Let us apply Algorithm~\ref{alg0} to the example shown in Figure~\ref{fig1}.
Node $B$ and $H$ have the same individual connectivity degree, i.e., $d_B=d_H$. As $g_H=2>g_B=1$, node $H$ becomes the cluster head and cluster $C_H$ is $\{H, B, A, G\}$.

@@

\section*{Proof of Theorem~\ref{clustering:theorem}}
\label{proof_clustering:theorem}
\begin{proof}
%Note that the formed cluster can be a singleton cluster, \ie cluster size is 1.
We consider a CRN which can be represented as a connected graph. (COMMENT: Why is it necessarily connected? No special case where the graph has two components?)
To simplify the discussion, we assume the secondary users have unique individual connectivity degrees. Each user has an identical ID and a social connectivity degree.
This assumption is fair as the social connectivity degrees and node ID are used to break ties in Algorithm~\ref{alg0}, when the individual connectivity degrees are unique, it is not necessary to use the former two metrics. (COMMENT: What do you mean by breaking ties?? I don't see why your argument holds.)

%we assume every node has at least one neighbour.
For the sake of contradiction, let us assume there exist some secondary user $\alpha$ which is not included into any cluster.
Then there is at least one node $\beta\in \text{Nb}_\alpha$ such that $d_{\alpha} > d_{\beta}$. Now, we distinguish between two cases: 
%Otherwise, node $\alpha$ is eligible to form a cluster. COMMENT: unnecessary sentence!
If $\beta$ becomes cluster head, node $\alpha$ is included.
If $\beta$ is not a cluster head, i.e., $\beta$ is not in any cluster (COMMENT: $\beta$ not being a cluster head and $\beta$ not belonging to any cluster is not the same statement!!!), we can repeat the previous analysis made on node $\alpha$, and deduce that node $\beta$ has at least one neighbouring node $\gamma$ with $d_{\gamma} < d_{\beta}$.
When no cluster head appears, this series (COMMENT: what is that? sequence?) of nodes with monotonically decreasing connectivity degrees might continue to grow. Finally, it ceases (COMMENT: not a good/suitable word!!) when either the individual connectivity degree is zero, or every secondary node has already been in the series (COMMENT: sequence?) of nodes.
An example of the formed node series is shown as Figure~\ref{lemma1}.

@@

Now, we can see that the node $\omega$ is the last element of this sequence.
As $\omega$ does not have neighboring nodes with lower individual connectivity degree $D$, $\omega$ becomes the cluster head and incorporate all its one-hop neighbours, including the node before (COMMENT: you mean $\alpha$?) it in the series (here we assume that every newly formed cluster has common channels).
After that, the node that joined a cluster will set its connection degree $D$ to $M$, which enables the node further down in the list (WHAT ??? What is further down and which list??? I cannot follow.) to become a cluster head.
In this way, all the nodes in the series are in at least one cluster in the inverse sequence (? inverse of?), which contradicts the assumption.
Meanwhile, through this proof, we know that within at most $N$ steps, all the nodes belong to certain clusters. (COMMENT: No, we don't! Where was that shown?)
\end{proof}

@@

Given a finite set $\mathcal{G} = \{ g_1, \ldots , g_N \} \subsetneq \mathbb{N}$ of non-negative integers and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ such that $S_i \subseteq \mathcal{G}$ for every $1 \leq i \leq N$.
Each set $S \in \mathcal{Q}$ is associated with a weight $w(S) \in \mathbb{R}$.
Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} w(S) > \lambda$.
\end{mydef}

Weighted k-set packing is NP-hard when $k\geqslant 3$.~\cite{Computers_a_Intractability}

To prove that the centralized clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is at least as hard as the latter.
%, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
%To complete the reduction, we need to conduct following two steps:
%\begin{itemize}
%\item Step 1: We show the existence a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
%\item Step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
%\end{itemize}
We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{S}$ (COMMENT: be careful - there is an overloading of $\mathcal{S}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering such that ... (to be completed - Erwin can do that)

%We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
%$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$. REPEATING THE DEF??
%Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
%$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$. COMMENT: again unnecessary. Already contained in the definition!
%As the number of common channel of clusters is always integer
%give new weight to them in following way

ERWIN FINISHED HERE FOR THE MOMENT ---
